First exclusive Deeply Virtual Compton Scattering measurement off bound nucleon in $^4$He

### 2018-07-05 eg6-letters/incoherent/incoherent_prl.tex
Final edits for RD

% DVCS selection
Incoherent DVCS events were selected by requiring an electron, a proton, and at 
least one photon in the final state. Electrons were identified as negatively 
charged tracks reconstructed in the drift chambers with an appropriate energy 
deposition in the electromagnetic calorimeter (EC) and a light yield above the 
threshold in the Cherenkov counters. The protons were identified from 
positively charged tracks based on their time-of-flight measured 
by the scintillator counters.  In addition, it was required that both the 
electron and the proton in the event originated from the same vertex at the 
target within CLAS tracking vertex resolution. The photons were detected in 
either the IC or the CLAS electromagnetic calorimeter. All the clusters within 
the IC fiducial region were assumed to be photons, while a timing cut is used 
to clean the EC photons from neutrons. Note that even though the DVCS reaction 
has only one real photon in the final state, events with more than one photon 
were not discarded at this stage. These extra photons are mostly soft photons from accidental 
coincidence which, as will be discussed below, the DVCS exclusivity cuts 
eliminate easily. In the following selection stage, the most energetic photon 
is considered as the DVCS photon candidate (see \cite{Hattawy:thesis} for 
additional details on the particles identification).

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with Q$^{2}$ greater the 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass (W$=(q+p)^2$) greater than 2 GeV to avoid the nucleon resonance region.  
The $t$, transferred momentum squared to the recoil proton by assuming an 
on-shell proton at rest, was required to be greater than a minimum allowed 
value at given Q$^2$ and W ($t~>~t_{min}$).  Then, the exclusivity of the 
incoherent DVCS events was ensured by imposing constraints on the kinematical 
variables resulting from conserving the four-momentum in the reaction 
$ep\rightarrow e'p'\gamma$. These kinematical variables are: the coplanarity 
angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) 
planes, the missing energy, mass, and transverse momentum of the $e'\gamma$ and 
$e'p'\gamma$ systems, the missing mass squared of the $e'p'$ system, and the 
angle $\theta$ between the measured photon and the missing momentum of the 
$e'p'$ system. The experimental data for the most relevant exclusivity 
variables and applied cuts are shown in FIG.~\ref{fig:kin-cuts} (see 
\cite{Hattawy:thesis} for additional details). We also rejected events where a 
$\pi^0$ was identified by the invariant mass of two photons. At the end of
this selection process, about 30k events 
passed all the requirements; their kinematic distributions are shown in 
FIG.~\ref{fig:kin-coverage}.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/incoh_exc_cuts_final.pdf}
\caption{The incoherent DVCS exclusivity cuts. The black distributions 
   represent the incoherent DVCS events candidate before all the exclusive 
   cuts. The shaded distributions represent the incoherent DVCS events which 
   passed all the exclusivity cuts except the quantity plotted. The vertical 
   red-dashed lines represent the applied exclusivity cuts. The distributions 
   from left to right and from top to bottoms are: $\Delta \phi$, missing 
   energy, missing masses squared and the cone angle ($\theta$) between the 
   measured and the calculated photons in the $e'p'$ final-state system. }
\label{fig:kin-cuts}

@@

%background
The two main backgrounds that contribute to the event sample after the exclusivity cuts are  
due to accidental coincidences and exclusive $\pi^0$ production where one of the photons 
from the $\pi^0$ decay escapes the detection. The contribution from accidental events, i.e., $e'p'\gamma$ collections 
with particles originating from different electron scatterings,
was evaluated to be of 6.5\% by selecting events passing all our selection cuts but originating from 
different vertices. The $\pi^0$ contamination was estimated using detector simulation and experimental 
data. From simulation, we calculated the ratio ($R$) of the number of $\pi^0$ 
events that are wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the 
number of events correcltly identified as exclusive $ep\rightarrow e'p'\pi^0$, 
$R = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$. Then in each kinematical bin and for 
each beam-helicity state, the $\pi^0$-subtracted experimental DVCS events is 
calculated as $N = N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow 
e'p'\pi^0}_{exp}$, where $N^{ep\rightarrow e'p'\gamma}_{exp}$ is the 
experimentally identified number of $ep\rightarrow e'p'\gamma$ and 
$N^{ep\rightarrow e'p'\pi^0}_{exp}$ is the experimentally identified 
$ep\rightarrow e'p'\pi^0$. Depending on the 
kinematics, we found this contamination to be of 8 to 10\%.

@@

In the kinematical phase-space of our experiment, the GPD $H$ dominates the 
contribution in the BSA over the other three GPDs. Therefore, 
the $\phi$ dependence of $A_{LU}$ gives a direct access to the real and 
imaginary part of the CFF $\mathcal{H}$ through the parameters $a_0$, $a_1$, 
and $a_2$ of equation \ref{eq:alu-simp}. The studies of  the free proton 
$A_{LU}$ measurements, \cite{Girod:2007aa}, have shown that the the pure DVCS 
contribution, $cos(2\phi)$ term ($a_2$), is suppressed and compatible with 
zero.

%{\bf Raphael: This paragraph is very confusing, is it true that a1 and a2 are 
%dominated by H? Do we have equivalents of eq. 3 for those? I actually did 
%notfind it in ref 31, which we are referring and we are also not using the 
%same definition of Im(H)...}

Due to limited statistics, the data were binned two-dimensionally into 36 bins.  
That is, four statistically-equivalent bins in one of the kinematical 
variable of interest -- $Q^{2}$, $x_{B}$ or $t$ -- were constructed, then each 
bin is divided into nine bins in the azimuthal angle ($\phi$).  
FIG.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
$\phi$ in bins of $Q^{2}$, $x_{B}$, and $t$. The curves on the plots are fits 
of the form $\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$. The main contributions 
to systematic uncertainties on these fits are from the choice of the DVCS 
exclusivity cuts (6\%) and the large binning size (7\%). Added quadratically, 
these uncertainties sum up to less than 10\% for all data points and remain 
significantly smaller than the statistical errors.

@@

We present in FIG.~\ref{fig:alu90} the dependence of the fitted $A_{LU}$ 
signals at $\phi$~=~90$^{\circ}$ on the kinematical variables $Q^2$, $x_{B}$, 
and $t$. Within the given uncertainties, $A_{LU}$ does not indicate a strong 
dependence on $Q^2$. The $x_{B}$ and $t$ dependencies are compared to 
theoretical calculations performed by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. Their model uses a realistic spectral function and 
considers off-shell effects. The calculations are carried out at slightly 
different kinematics than our data but still provide important guidance. The 
experimental results appear to have smaller asymmetries especially at low 
$x_{B}$ than the calculations.  These differences may arise from nuclear 
effects which are not taken into account in the model, such as long-range 
interactions.  On the graph for $-t$ dependence, we show previous measurements 
by the HERMES collaboration \cite{Airapetian:2009cga} using inclusive final 
state, ($e^\prime\gamma$). Due to large experimental uncertainties of HERMES 
points, the two measurements do not disagree, but we can also see that their 
high $-t$ results were smaller than expected by models.

@@

In this work we carried out the first step towards measuring the 
``generalized'' EMC effect in order to understand the potential sources of 
nuclear effects at the partonic level within the GPDs framework. We construct 
the ratio of $A_{LU}$ for bound protons to that on free proton target measured 
using similar electron-beam energy and experimental setup.  
FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the dependence of the 
BSA ratio at $\phi$~=~90$^{\circ}$ on the kinematical variables 
$Q^2$, $x_B$, and $t$. The free proton asymmetries were interpolated from the 
published results \cite{Girod:2007aa}.

\begin{figure}[tb]
\centering
%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_Q2_shortscenrario.pdf}\\
%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}\\
\includegraphics[width=8.5cm]{figs/ALU_ratioInc_t_shortscenrario.pdf}
\caption{ The $A_{LU}$ ratio of the bound to the free proton at 
   $\phi$~=~90$^{\circ}$ as a function of $t$. The black squares are from this 
   work, the green circles are the HERMES inclusive measurement 
   \cite{Airapetian:2009cga}. The blue and red curves are results of off-shell 
   calculations \cite{simonetta_2}. The solid and dashed black curves are from 
   on-shell calculations \cite{Guzey:2008fe}.} 
   \label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}

The $A_{LU}$ ratios show a 20\%-40\% lower asymmetries for a bound proton compared 
to the free proton. The measurements disagree with the off-shell \cite{simonetta_2} 
and the on-shell calculations that use the medium modified GPDs as calculated from 
the quark-meson coupling model \cite{Guzey:2008fe}. In particular, at lower $x_B$, 
where the off-shell model predicts an enhancement of the ratio, our experiment 
shows a sharp drop. This measurement shows that an important nuclear effect is
missing from the existing models in order to explain this strong quenching of
the BSA.

%conclusion
In summary, we have presented our BSA measurements 
associated with incoherent DVCS off $^4$He using an upgraded setup of the CLAS 
spectrometer at Jefferson Lab. Our results were compared to model 
calculations based on different assumptions of the nuclear medium effects at 
the partonic level.  The bound-proton 
BSA is largely suppressed compared to the free proton 
results measured in a similar phase-space. This surprising result opens a new avenue 
for progress in the understanding of the quarks and gluons behavior in the
nuclear medium.

@@

\bibitem{Hattawy:thesis}
M.~Hattawy, Ph.D. thesis, Universit{\'e} Paris Sud - Paris XI, France, 2015 
[Institution Report No. 2015PA112161].

>>>>

% DVCS selection
Incoherent DVCS events were selected by requiring an electron, a proton, and at 
least one photon in the final state. Electrons were identified as negatively 
charged tracks reconstructed in the drift chambers with an appropriate energy 
deposition in the electromagnetic calorimeter (EC) and a light yield above the 
threshold in the Cherenkov counters. The protons were identified from 
positively charged tracks based on their time-of-flight measured 
by the scintillator counters.  In addition, it was required that both the 
electron and the proton in the event originated from the same vertex at the 
target. The photons were detected in 
either the IC or the CLAS electromagnetic calorimeter. All the clusters within 
the IC fiducial region were assumed to be photons, while a timing cut is used 
to clean the EC photons from neutrons. Note that even though the DVCS reaction 
has only one real photon in the final state, events with more than one photon 
were not discarded at this stage. These extra photons are mostly soft photons from accidental 
coincidence which, as will be discussed below, the DVCS exclusivity cuts 
eliminate easily. In the following selection stage, the most energetic photon 
is considered as the DVCS photon candidate (see \cite{Hattawy:thesis} for 
additional details on the particles identification).

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with Q$^{2}$ greater the 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass (W$=(q+p)^2$) greater than 2 GeV to avoid the nucleon resonance region.  
The $t$, transferred momentum squared to the recoil proton assuming an 
on-shell proton at rest, was required to be greater than a minimum allowed 
value at given Q$^2$ and W ($t~>~t_{min}$).  Then, the exclusivity of the 
incoherent DVCS events was ensured by imposing constraints on the kinematical 
variables resulting from conserving the four-momentum in the reaction 
$ep\rightarrow e'p'\gamma$. These kinematical variables are: the coplanarity 
angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) 
planes, the missing energy, mass, and transverse momentum of the $e'\gamma$ and 
$e'p'\gamma$ systems, the missing mass squared of the $e'p'$ system, and the 
angle $\theta$ between the measured photon and the missing momentum of the 
$e'p'$ system. The experimental data for the most relevant exclusivity 
variables are shown in FIG.~\ref{fig:kin-cuts}. We also rejected events where a 
$\pi^0$ was identified by the invariant mass of two photons. At the end of
this selection process, about 30k events 
passed all the requirements; their kinematic distributions are shown in 
FIG.~\ref{fig:kin-coverage}.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/incoh_exc_cuts_final.pdf}
\caption{The distributions 
   from left to right and from top to bottoms are: $\Delta \phi$, missing 
   energy, missing masses squared and the cone angle ($\theta$) between the 
   measured and the calculated photons in the $e'p'$ final-state system.
   The incoherent DVCS exclusivity cuts are represented by the vertical 
   red-dashed lines. The black distributions 
   represent the incoherent DVCS events candidate before the exclusivity 
   cuts. The shaded distributions represent the incoherent DVCS events which 
   passed all these cuts except the quantity plotted.}
\label{fig:kin-cuts}

@@

%background
The two main backgrounds that contribute to the event sample after the exclusivity cuts are  
due to accidental coincidences and exclusive $\pi^0$ production where one of the photons 
from the $\pi^0$ decay escapes the detection. The contribution from accidental events, i.e., $e'p'\gamma$ collections 
with particles originating from different electron scatterings,
was evaluated to be of 6.5\% by selecting events passing all our selection cuts but originating from 
different vertices. The $\pi^0$ contamination was estimated using detector simulation and experimental 
data. From simulation, we calculated the ratio ($R$) of the number of $\pi^0$ 
events that are wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the 
number of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$, 
$R = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$. Then in each kinematical bin and for 
each beam-helicity state, the $\pi^0$-subtracted experimental DVCS events is 
calculated as $N = N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow 
e'p'\pi^0}_{exp}$, where $N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is the 
number of $ep\rightarrow e'p'\gamma$ ($ep\rightarrow e'p'\pi^0$) experimentally identified. Depending on the 
kinematics, we found this contamination to be of 8 to 10\%.

@@

In the kinematical phase-space of our experiment, the GPD $H$ is
expected to dominate the 
contribution in the BSA over the other three GPDs. There, 
the $\phi$ dependence of $A_{LU}$ is mostly sensitive to the  
imaginary part of the CFF $\mathcal{H}$ through the parameters $a_0$ of 
equation~\ref{eq:alu-simp}. The measurement of the free proton 
$A_{LU}$ \cite{Girod:2007aa} has confirmed that the $a_0$ term is 
dominating the shape of the distribution.

Due to limited statistics, the data were binned two-dimensionally into 36 bins.  
That is, four bins in one of the kinematical variable of interest ($Q^{2}$, 
$x_{B}$ or $t$) and nine bins in the azimuthal angle ($\phi$).  
FIG.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
$\phi$ in bins of $Q^{2}$, $x_{B}$, and $t$. The curves on the plots are fits 
of the form $\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$. The main contributions 
to systematic uncertainties on these fits are from the choice of the DVCS 
exclusivity cuts (6\%) and the large binning size (7\%). The systematic uncertainties
sum up to less than 10\% for all data points and thus always remain significantly 
smaller than the statistical errors.

@@

We present in FIG.~\ref{fig:alu90} the dependence of the fitted $A_{LU}$ 
signals at $\phi$~=~90$^{\circ}$ on the kinematical variables $Q^2$, $x_{B}$, 
and $t$. Within the given uncertainties, $A_{LU}$ does not indicate a strong 
dependence on $Q^2$. The $x_{B}$ and $t$ dependencies are compared to 
theoretical calculations performed by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. Their model uses nuclear spectral function and 
considers mainly off-shell effects. The calculations are carried out at slightly 
different kinematics than our data but still provide important guidance. The 
experimental results appear to have smaller asymmetries especially at low 
$x_{B}$ than the calculations. These differences may arise from nuclear 
effects which are not taken into account in the model, such as long-range 
interactions. On the graph for $-t$ dependence, we show previous measurements 
by the HERMES collaboration \cite{Airapetian:2009cga}, in which only electrons
and photons were measured. Due to the large experimental uncertainties of the HERMES 
points, the two measurements are completely compatible.

@@

One can use the nuclear DVCS to measure a ``generalized'' EMC effect in order 
to see if significant nuclear effects are also visible within the GPD framework. 
To explore this idea, we construct 
the ratio of $A_{LU}$ for bound protons to that on free proton target.  
FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the 
BSA ratio based on interpolation of the free proton asymmetries from  
CLAS \cite{Girod:2007aa} as a function of the kinematical variable
$x_B$. The $A_{LU}$ ratios show a 20\%-40\% lower asymmetries for a bound proton compared 
to the free proton mirroring a form of EMC effect but with a surprising 
large effect, in particular at low $x_B$. The measurements disagree with the off-shell \cite{simonetta_2} 
and the on-shell calculations that use the medium modified GPDs as calculated from 
the quark-meson coupling model \cite{Guzey:2008fe}. In particular, the difference becomes
large at lower $x_B$, 
where the off-shell model predicts an enhancement of the ratio, where our experiment 
shows a sharp drop. This measurement shows that an important nuclear effect is
missing from the existing models in order to explain this strong quenching of
the BSA.

\begin{figure}[tb]
\centering
%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_Q2_shortscenrario.pdf}\\
\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}
%\includegraphics[width=8.5cm]{figs/ALU_ratioInc_t_shortscenrario.pdf}
\caption{ The $A_{LU}$ ratio of the bound to the free proton at 
   $\phi$~=~90$^{\circ}$ as a function of $x_B$. The black squares are from this 
   work, the green circle is the HERMES measurement 
   \cite{Airapetian:2009cga}. The blue and red curves are results of off-shell 
   calculations \cite{simonetta_2}. The solid and dashed black curves are from 
   on-shell calculations \cite{Guzey:2008fe}.} 
   \label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}

%conclusion
In summary, we have presented our BSA measurements 
associated with incoherent DVCS off $^4$He using an upgraded setup of the CLAS 
spectrometer at Jefferson Lab. Our results were compared to model 
calculations based on different assumptions of the nuclear medium effects at 
the partonic level. The bound-proton BSA is largely suppressed compared to 
the free proton BSA. This surprising result opens a new avenue 
for progress in the understanding of the quarks and gluons behavior in the
nuclear medium.

@@
